Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureExtracR]

### 2023-08-07 tutorial/05-evaluation.qmd
tutorial updated

```{r}
#| label: tbl-cluster-performance

@@

df_kmeans_performance %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = "c",
      digits = 2,
      row.names = FALSE,
      col.names = kmeans_metrics_names,
      caption = "Cluster Performance for the $k$ = 2–10") %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  ) %>%
  scroll_box(width = "100%", height = "500px")
```

>>>>

```{r}
#| label: tbl-cluster-performance
#| fig-cap: Cluster Performance for the k = 2–10

@@

df_kmeans_performance %>%
  kbl(.,
      escape = FALSE,
      booktabs = T,
      align = "c",
      digits = 2,
      row.names = FALSE,
      col.names = kmeans_metrics_names) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  ) %>%
  scroll_box(width = "100%")
```

### 2023-08-07 tutorial/about.qmd
tutorial updated

The full code of this illustration as well as the main manuscript is available as part of [our GitHub repository](https://github.com) [@KreienkampMasked-clust-github]. A minimal version of the code as well as an archive file are available in [our Open Science ](https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4) [@KreienkampMasked-clust-osf]. For convenience purposes, we have also collected a number of functions we created as part of the illustration as an R-package. This package is available as its own GitHub repository and can be downloaded with the `devtools` package as `tsFeatureExtracR`: `devtools::install_github("JannisCodes/tsFeatureExtracR")` [@KreienkampBlinded2023-tsFeatureExtracR].

>>>>

The full code of this illustration as well as the main manuscript is available as part of [our GitHub repository](https://github.com) [@KreienkampMasked-clust-github]. A minimal version of the code as well as an archive file are available in [our Open Science ](https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4) [@KreienkampMasked-clust-osf]. For convenience purposes, we have also collected a number of functions we created as part of the illustration as an R-package. This package is available as its own GitHub repository and can be downloaded with the `devtools` package `devtools::install_github("JannisCodes/tsFeatureExtracR")`, you can also [download the R package here](https://github.com/JannisCodes/tsFeatureExtracR/archive/refs/tags/v.0.1.0.tar.gz) [@KreienkampBlinded2023-tsFeatureExtracR].

### 2023-08-07 tutorial/index.qmd
tutorial updated

---
title: "Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureExtracR]"
author:
  - name: Jannis Kreienkamp
    orcid: 0000-0002-1831-5604
    email: j.kreienkamp@rug.nl
    corresponding: true
    # affiliations:
    #   - ref: rug
  - name: Maximilian Agostini
    orcid: 0000-0001-6435-7621
    # affiliations:
    #   - ref: rug
  - name: Rei Monden
    orcid: 0000-0003-1744-5447
    # affiliations:
    #   - ref: hu
  - name: Kai Epstude
    orcid: 0000-0001-9817-3847
    # affiliations:
    #   - ref: rug
  - name: Peter de Jonge
    orcid: 0000-0002-0866-6929
    # affiliations:
    #   - ref: rug
    #   - ref: icpe
  - name: Laura F. Bringmann
    orcid: 0000-0002-8091-9935
    # affiliations:
    #   - ref: rug
    #   - ref: icpe
# affiliations:
#   - id: rug
#     name: University of Groningen
#   - id: hu
#     name: Hiroshima University
#   - id: icpe
#     name: ICPE
---

>>>>

---
title: "Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureExtracR]"
author:
  - name: Masked for Peer Review
  - name: ██████ ██████████
    orcid: 0000-0000-0000-0000
  - name: ██████████ ████████
    orcid: 0000-0000-0000-0000
  - name: ███ ██████
    orcid: 0000-0000-0000-0000
  - name: ███ ███████
    orcid: 0000-0000-0000-0000
  - name: █████ ██ █████
    orcid: 0000-0000-0000-0000
  - name: █████ ██ █████████
    orcid: 0000-0000-0000-0000
  # - name: Jannis Kreienkamp
  #   orcid: 0000-0002-1831-5604
  #   email: j.kreienkamp@rug.nl
  #   corresponding: true
  #   # affiliations:
  #   #   - ref: rug
  # - name: Maximilian Agostini
  #   orcid: 0000-0001-6435-7621
  #   # affiliations:
  #   #   - ref: rug
  # - name: Rei Monden
  #   orcid: 0000-0003-1744-5447
  #   # affiliations:
  #   #   - ref: hu
  # - name: Kai Epstude
  #   orcid: 0000-0001-9817-3847
  #   # affiliations:
  #   #   - ref: rug
  # - name: Peter de Jonge
  #   orcid: 0000-0002-0866-6929
  #   # affiliations:
  #   #   - ref: rug
  #   #   - ref: icpe
  # - name: Laura F. Bringmann
  #   orcid: 0000-0002-8091-9935
  #   # affiliations:
  #   #   - ref: rug
  #   #   - ref: icpe
# affiliations:
#   - id: rug
#     name: University of Groningen
#   - id: hu
#     name: Hiroshima University
#   - id: icpe
#     name: ICPE
---
